%ack
\pagebreak
\vspace*{-1.0 cm}
\begin{centering}
\textbf{ ACKNOWLEDGEMENT} \\[2.0 cm]
\end{centering}

This project aims for  \textsc{Chatbot using Natural Language Processing}. The project scope was very vast, but I've tried to it to the best of my ability and knowledge.\\I would like to thank a few people who have helped me for this project.\\

\begin{itemize}
\item My guide, \emph{Mr. Deepak kant Netam} for directing me as to how to go about the project and helping me in figuring out different approaches for the problem at hand.

\item \emph{Dr. Amit Khaskalam}, Head of Information Technology Department, for giving us the opportunity to work on this project.

\item All the esteemed faculty members, \emph{Mr. Rajesh Mahule, Mr. Santosh Soni, Mr. Abhishek Jain, Mr. Agnivesh Pandey, Mr. Pankaj Chandra, Mr. Suhel Ahamed, Mr. Anand Rawal and Ms. Akanksha Gupta} for their continued support and effort.

\item The director of "Institute of Technology", \emph{Prof. Shailendra Kumar}, for providing all the necessary facilities.

\item The dean of "Institute of Technology", \emph{Prof. Mukesh Singh}, for providing constant support to students.

\item My \emph{friends}, for all the fruitful discussions on this topic, which proved very helpful. 

\item Last but not the least, my \emph{parents}, for their constant support and encouragement. \\

\end{itemize}

I would like to thank all those who spared their valuable time to discuss and helped me present the project in it's current shape and form.

\pagebreak
