\chapter{Introduction}

{ \bf What is chatbot? }\\

Chatbot stands for chatter robot. It is a computer program which has the ability to chat with human users. Audio or text can be used as medium of communication. The primary aim of writing these conversational programs is to have a powerful tool that chat in such a way that the human user cannot realize that he is talking to a software program. Chatbot programs are also referred to as Artificial Conversational Entities, talk bots, chatterbots and chatterboxes.\\
\\


\section{Background and Recent Research}

{ \bf Where is the state of art?}

\subsection{Literature Survey}

There are many types of Chat Bots, all with varying levels of complexity and strategies for tricking a human that they are not speaking to a computer.\\
\\
ELIZA being the first and most well known created in 1966, would play the part of a doctor and continue to push back the conversation to the user by asking how previous responses would make one feel by trying to dig deeper to the root of the problem. It was clever and also simple.\\
\\
CleverBot was brought online in 1997. It was designed to reply with input from some point from the past. Today, there are several million replies across many topics and domains. The input is sometimes on topic and relevant, and other times wildly way off topic. This approach is much like search results and without knowing the reason for asking the question in the first place, is it hard to provide accurate results.\\[1.0cm]


\subsection{Current scenario}

After reviewing the current landscape, it lead me to believe that fooling a human into thinking a bot is real was not because the bot was great, rather it employing silly tactics like deliberating using broken english, typos and deflection.\\[0.5cm]

The chatbot heyday, to the extent that it had one, peaked at the dawn of the Internet and with AOL chatrooms. Chatbots surfaced in programs, like Microsoft Word, which had Clippy, the virtual assistant. But chatbots never proved more useful than annoying and mostly faded, until today. Messaging apps like Facebook Messenger, Kik, Snapchat, WeChat, Viber, Skype and Line will collectively reach 2 billion users in the next two years. And chatbots are seen as one way for big brands and publishers to reach these users, one on one.\\

Eugene Goostman made the news a few months back as being ‘turing complete’ which created controversy. This bot employs several tricks such as pretending to be a 13-year-old boy who’s english is his second language.\\

Chat bots have to be great at answering questions, this is usually how they are challenged, and IBM’s Watson is probably the best question and answer system. However unlike Watson, we don’t need to be 100 \% accurate when it comes to answering questions.We can significantly reduce the knowledge base that drives the bot, after all, nobody likes a no-it-all.\\



\section{Motivation}

Human interaction has always fascinated me: social awkwardness, communication style, how knowledge is transferred, how relationships are built around trust, story telling and knowledge exchange.\\ \\
What if a machine invoked an emotional response?\\[0.5cm]

{\bf First the back story} \\

I want to write about a project I have been working on, and how it has engulfed the last few years of my life, but ultimately, this post is about creating a real chat bot.\\
\\
Work to date has been an extension of the work done in NLP (natural language process), currently a collection of tools now forming the foundation of Node/Natural.\\
\\
My initial goal was to build a IBM Watson type clone; something that could parse input in some form and sort out candidates from a data source. \\

I did some research in language and how communication is affected. For example people who are tired, or introverted tend to give shorter answers when conversing. I spent a fair amount of time thinking about how this would play into a Chat Bot.
 \\
